---
title: "Registrar Project Visualisations"
output: html_notebook

---

Project visualisations

#LOAD PACKAGES

```{r}

#install.packages("ggplot2")

library(ggplot2)

library(egg)


```

#LOAD THE DATA

## College information data
```{r}
#give the dataset a name 

data1 <- read.csv(file='Outputs/included_data.csv')

#read the first ten rows of data

#data1[1:10,]

#dim(data1)

#names(data1)

```


## Datafames with and without projects

Create dataframes for data with and without projects

```{r}
#with projects
data <- subset(data1, scholarly_project == "True"|scholarly_project =="False")

#without projects
dataNOPROJ <- subset(data1, scholarly_project =="False")

head(data)

```



## Blooms Taxonomy

###Wrangle the data

With a project:

```{r}
#create table of colleges, level and constructive alignment type and frequencies

table_competency_level <- data.frame(with(data, table(College_ID, Competency, constructive_type_abv)))

head(table_competency_level)

#Order of constructive type to LO, LA and AA
table_competency_level$constructive_type_abv  <- factor(table_competency_level$constructive_type_abv , levels = c("LO","LA", "AA"))

table_competency_level <- table_competency_level[order(table_competency_level$constructive_type_abv), ]

head(table_competency_level)



```


Without project:

```{r}

#create table of colleges, level and constructive alignment type


table_competency_level1 <- data.frame(with(dataNOPROJ, table(College_ID, Competency, constructive_type_abv)))

#Order of constructive type to LO, LA and AA
table_competency_level1$constructive_type_abv  <- factor(table_competency_level1$constructive_type_abv , levels = c("LO","LA", "AA"))

table_competency_level1 <- table_competency_level1[order(table_competency_level1$constructive_type_abv), ]




#get ids of colleges who only have project affiliated data
no_proj_IDs <- unique(table_competency_level$College_ID) [!(unique(table_competency_level$College_ID)  %in% unique(table_competency_level1$College_ID) )]

#get blooms levels
blooms_levels <- unique(table_competency_level1$Competency)

#get constuctive alignment levels
constructive_type_abv_levels <- unique(table_competency_level1$constructive_type_abv)


#copy dataframe
df <- table_competency_level1[0,]

#add in data
for (i in no_proj_IDs){
  
  for (j in blooms_levels){
    
    df1 <- data.frame(i, j, constructive_type_abv_levels, 0)
    
    names(df1) <- colnames(df)
    
    df <- rbind(df, df1)
    
    
  }
  
}

#add missing data to table with out project freq
table_competency_level1 <- rbind(table_competency_level1, df)


```





```{r}

###########WITH PROJECT############################

#facet the heat map
#https://jcoliver.github.io/learn-r/006-heatmaps.html


#order facet grid
#https://stackoverflow.com/questions/14262497/fixing-the-order-of-facets-in-ggplot
table_competency_level$Competency_f = factor(table_competency_level$Competency, 
                                             #create the order
                                             levels=c("Remembering", "Understanding", "Applying", "Analysing", "Evaluating", "Creating"))


#order y axis
table_competency_level$College_ID = factor(table_competency_level$College_ID, 
                                             #create the order
                                             levels=c(rev(seq(1, length(unique(table_competency_level$College_ID)), 1))))


#WITH SCHOLARLY PROJECTS
#create heatmap
bloomsProj.heatmap <- ggplot(data = table_competency_level, 
                       mapping = aes(x = constructive_type_abv,
                                     y = College_ID,
                                     fill = Freq)) + #order the y axis #https://stackoverflow.com/questions/57177068/how-to-set-specific-order-of-variables-on-y-axis-in-a-heatmap
  #add tiles
  geom_tile() +
  
  #change the x label
  xlab(label = "Competency") +
  
  #create the facet grid
  facet_grid(~ Competency_f, switch = "x", scales = "free_x", space = "free_x")+
  
  #change the colours
scale_fill_gradient(name = "Freq", 
                      low = "#f7fbff", 
                      high = "#081d58") +
  
  
  #place lines on the outside of each competency level
  theme(strip.placement = "outside",
        
        #remove the legend as the numbers are not so relevant
        legend.position = "none") +
  
  #change y label
  ylab("College")+
  
  #change x label
  xlab("\n LO = Learning Objective \n LA = Learning Activity \n AA = Assessment Activity")+
  
  #change size of x label
  theme(axis.title.x = element_text(size = 8))+
  
  #add a title
  ggtitle(label = "Constructive alignment across Bloom's Taxonomy \n with scholarly project Learning and Assessment activities") +
  
  
  theme_bw()

#save the file (https://stackoverflow.com/questions/30383710/ggplot2-file-output-issues)
ggsave(file = "Outputs/competencyHeat_withProj.png", dpi = 600, width = 10, height = 10, units = "in")

bloomsProj.heatmap


#dev.off()


###########WITHOUT PROJECT############################


#order facid grid
table_competency_level1$Competency_f = factor(table_competency_level1$Competency, 
                                             #create the order
                                             levels=c("Remembering", "Understanding", "Applying", "Analysing", "Evaluating", "Creating"))



#order y axis
table_competency_level1$College_ID = factor(table_competency_level1$College_ID, 
                                             #create the order
                                             levels=c(rev(seq(1, length(unique(table_competency_level1$College_ID)), 1))))



bloomsNOProj.heatmap <- ggplot(data = table_competency_level1, 
                       mapping = aes(x = constructive_type_abv,
                                     y = College_ID,
                                     fill = Freq)) +
  #add tiles
  geom_tile() +
  
  #change the x label
  xlab(label = "Competency") +
  
  #create the facet grid
  facet_grid(~ Competency_f, switch = "x", scales = "free_x", space = "free_x")+
  
  #change the colours
scale_fill_gradient(name = "Freq", 
                      low = "#f7fbff", 
                      high = "#081d58") +
  
  #place lines on the outside of each competency level
  theme(strip.placement = "outside",
        
        #remove the legend as the numbers are not so relevant
        legend.position = "none") +
  
  #change y label
  ylab("College")+
  
  #change x label
  xlab("\n LO = Learning Objective \n LA = Learning Activity \n AA = Assessment Activity")+
  
  #change size of x label
  theme(axis.title.x = element_text(size = 8))+
  
  #add a title
  ggtitle(label = "Constructive alignment across Bloom's Taxonomy \n without scholarly project Learning and Assessment activities") +
  
  
  theme_bw()

#save the file (https://stackoverflow.com/questions/30383710/ggplot2-file-output-issues)
ggsave(file = "Outputs/competencyHeat_NOPROJ.png", dpi = 600, width = 10, height = 10, units = "in")


#bloomsNOProj.heatmap
#install.packages("gridExtra")
#library(gridExtra)


#grid.arrange(bloomsProj.heatmap, bloomsNOProj.heatmap, ncol= 2, nrow = 1)


```

```{r}



```



#### Combined Heatmap

https://stackoverflow.com/questions/38856309/r-grid-arrange-marginal-plots-to-ggplot2-heatmap-geom-tile

```{r}

#prepare clean graphs

#heatmap WITH project
bloomsProj.heatmap.clean <- bloomsProj.heatmap +
  theme(axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
          legend.position="none") +
  labs(title = "With project")
  
  ggtitle(element_blank())




bloomsProj.heatmap.clean



#heat withOUT project

#heatmap WITH project
bloomsNOProj.heatmap.clean <- bloomsNOProj.heatmap +
  theme(axis.title.y = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
        
        
              ) +
  labs(title = "WithOUT project")
  


bloomsNOProj.heatmap.clean


  

```




https://stackoverflow.com/questions/38856309/r-grid-arrange-marginal-plots-to-ggplot2-heatmap-geom-tile


https://cran.r-project.org/web/packages/lemon/vignettes/legends.html



```{r}

final_plot<- ggarrange(bloomsProj.heatmap.clean,
                       bloomsNOProj.heatmap.clean,
                        
                       #catagorical_publish_graph.clean.leg,
                       #training_graph.clean.leg,
                       #supervisor_graph.clean.leg,
                       
                       
                       nrow = 1, ncol = 2, widths = c(30, 30), heights = c(20))


#gtable_show_layout(final_plot)




#save graph
ggsave(file = "Outputs/combined_blooms.png", 
       final_plot,
       dpi = 600, width = 100, height = 50, units = "cm", limitsize = FALSE)

```



## Research Level

### Wrangle the data

With projects:

```{r}

#create table of colleges, level and constructive alignment type

table_research_level <- data.frame(with(data, table(College_ID, Research.Level, constructive_type_abv)))

#head(table_research_level)

```


```{r}
#Order of constructive type to LO, LA and AA
table_research_level$constructive_type_abv  <- factor(table_research_level$constructive_type_abv , levels = c("LO","LA", "AA"))

table_research_level <- table_research_level[order(table_research_level$constructive_type_abv), ]

#head(table_research_level)
```


Without project

```{r}

#create table of colleges, level and constructive alignment type

table_research_level1 <- data.frame(with(dataNOPROJ, table(College_ID, Research.Level, constructive_type_abv)))

#head(table_research_level1)


#Order of constructive type to LO, LA and AA
table_research_level1$constructive_type_abv  <- factor(table_research_level1$constructive_type_abv , levels = c("LO","LA", "AA"))

table_research_level1 <- table_research_level1[order(table_research_level1$constructive_type_abv), ]

#head(table_research_level1)






#get ids of colleges who only have project affiliated data
no_proj_IDs <- unique(table_research_level$College_ID) [!(unique(table_research_level$College_ID)  %in% unique(table_research_level1$College_ID) )]

#get research levels
research_levels <- unique(table_research_level1$Research.Level)

#get constuctive alignment levels
constructive_type_abv_levels <- unique(table_research_level1$constructive_type_abv)


#copy dataframe
df <- table_research_level1[0,]

#add in data
for (i in no_proj_IDs){
  
  for (j in research_levels){
    
    df1 <- data.frame(i, j, constructive_type_abv_levels, 0)
    
    names(df1) <- colnames(df)
    
    df <- rbind(df, df1)
    
    
  }
  
}

#add missing data to table with out project freq
table_research_level1 <- rbind(table_research_level1, df)




```



### Draw the heatmaps

Create the heatmaps
```{r}

###########WITH PROJECT############################

#https://jcoliver.github.io/learn-r/006-heatmaps.html


#order facet drid
#https://stackoverflow.com/questions/14262497/fixing-the-order-of-facets-in-ggplot
table_research_level$Research.Level_f = factor(table_research_level$Research.Level, levels=c('Using','Participating','Leading','Undef'))



#order y axis
table_research_level$College_ID = factor(table_research_level$College_ID, 
                                             #create the order
                                             levels=c(rev(seq(1, length(unique(table_research_level$College_ID)), 1))))


#create heatmap
researchLevelProj.heatmap <- ggplot(data = table_research_level, mapping = aes(x = constructive_type_abv,
                                                       y = College_ID,
                                                       fill = Freq)) +
  geom_tile() +
  xlab(label = "Research Level") +
  facet_grid(~ Research.Level_f) +
facet_grid(~ Research.Level_f, switch = "x", scales = "free_x", space = "free_x")+

  #add colors
  scale_fill_gradient(name = "Freq", 
                      low = "#f7fbff", 
                      high = "#081d58") +

theme(strip.placement = "outside",
      
      #remove the legend as the numbers are not so relevant
        legend.position = "none") +
  
  #change y label
  ylab("College")+
  
  #change x label
  xlab("\n LO = Learning Objective \n LA = Learning Activity \n AA = Assessment Activity")+
  
  #change size of x label
  theme(axis.title.x = element_text(size = 8))+
  
  #add a title
  ggtitle(label = "Constructive alignment across research levels \n with scholarly project Learning and Assessment activities")+
  
  
  theme_bw()

#save the file (https://stackoverflow.com/questions/30383710/ggplot2-file-output-issues)
ggsave(file = "Outputs/ResearchLevelHeat_withProj.png", dpi = 600, width = 10, height = 10, units = "in")



researchLevelProj.heatmap


#dev.off()


###########WITHOUT PROJECT############################

#https://jcoliver.github.io/learn-r/006-heatmaps.html


#order facet grid
#https://stackoverflow.com/questions/14262497/fixing-the-order-of-facets-in-ggplot
table_research_level1$Research.Level_f = factor(table_research_level1$Research.Level, levels=c('Using','Participating','Leading','Undef'))



#order y axis
table_research_level1$College_ID = factor(table_research_level1$College_ID, 
                                             #create the order
                                             levels=c(rev(seq(1, length(unique(table_research_level1$College_ID)), 1))))


#create heatmap
researchLevelNOProj.heatmap <- ggplot(data = table_research_level1, mapping = aes(x = constructive_type_abv,
                                                       y = College_ID,
                                                       fill = Freq)) +
  geom_tile() +
  xlab(label = "Research Level") +
  facet_grid(~ Research.Level_f) +
facet_grid(~ Research.Level_f, switch = "x", scales = "free_x", space = "free_x")+

  #add colours
  scale_fill_gradient(name = "Freq", 
                      low = "#f7fbff", 
                      high = "#081d58") +

theme(strip.placement = "outside",
      
      #remove the legend as the numbers are not so relevant
        legend.position = "none") +
  
  #change y label
  ylab("College")+
  
  #change x label
  xlab("\n LO = Learning Objective \n LA = Learning Activity \n AA = Assessment Activity")+
  
  #change size of x label
  theme(axis.title.x = element_text(size = 8))+
  
  ggtitle(label = "Constructive alignment across research levels \n without scholarly project Learning and Assessment activities")+
  

  
  theme_bw()

#save the file (https://stackoverflow.com/questions/30383710/ggplot2-file-output-issues)
ggsave(file = "Outputs/ResearchLevelHeat_NOPROJ.png", dpi = 600, width = 10, height = 10, units = "in")



researchLevelNOProj.heatmap




#dev.off()


```

#### Combined Heatmap

https://stackoverflow.com/questions/38856309/r-grid-arrange-marginal-plots-to-ggplot2-heatmap-geom-tile

```{r}

#prepare clean graphs

#heatmap WITH project
researchLevelProj.heatmap.clean <- researchLevelProj.heatmap +
  theme(axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
          legend.position="none") +
  labs(title = "With project")
  
  ggtitle(element_blank())




researchLevelProj.heatmap.clean



#heat withOUT project

#heatmap WITH project
researchLevelNOProj.heatmap.clean <- researchLevelNOProj.heatmap +
  theme(axis.title.y = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
        
        
              ) +
  labs(title = "WithOUT project")
  


researchLevelNOProj.heatmap.clean



```




https://stackoverflow.com/questions/38856309/r-grid-arrange-marginal-plots-to-ggplot2-heatmap-geom-tile


https://cran.r-project.org/web/packages/lemon/vignettes/legends.html



```{r}

final_plot<- ggarrange(researchLevelProj.heatmap.clean,
                       researchLevelNOProj.heatmap.clean,
                        
                       #catagorical_publish_graph.clean.leg,
                       #training_graph.clean.leg,
                       #supervisor_graph.clean.leg,
                       
                       
                       nrow = 1, ncol = 2, widths = c(30, 30), heights = c(20))


#gtable_show_layout(final_plot)




#save graph
ggsave(file = "Outputs/combined_research_level.png", 
       final_plot,
       dpi = 600, width = 100, height = 50, units = "cm", limitsize = FALSE)

```



